Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
remark regarding the controller's precision

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
We compute the coefficients for $K$ in the domain $\mathbb{R}<I,F>$.

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. For this purpose, it assumes some
precision $<I_p,F_p>$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we considering the currently
assumed $<I_p,F_p>$, $k$ and sampling rate.

% The soundness is to be 
% restored by the subsequent three validation stages.

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Our synthesis problem}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
The synthesis problem we are trying to solve is the following:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be 0 (\todo{refer to wherever this is explained initially}).
Then, when mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I,F\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$. For this purpose, it assumes some
precision $\langle I_p,F_p\rangle$ for the plant, a $k$ and a sampling rate.  The
checks that these assumptions are sound are performed by subsequent
{\sc verify} stages.

2. The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$ is safe for all possible initial states, i.e., does not reach an unsafe
state within $k$ steps. 
This check is potentially unsound because we consider the currently
assumed $<I_p,F_p>$, $k$ and sampling rate.
